Extending EAGGA to Neural Networks

### 2025-03-05 paper/main.tex
restructure sections a little, add some more bullets

\section{Introduction}

@@

\subsection{Tabular Data}
- most common type of data
- bad performance of deep learning models on tabular data

@@

\subsection{Automated Machine Learning (AutoML)}
\subsubsection{Hyperparameter Optimization (HPO)}
- grid + random search
- Bayesian optimisation
  * short intro
  * why is it unsuitable for our task? (makes no sense to have it here, unless we introduce our problem (feature selection is high-dim binary space) in the introduction)
- evolutionary algorithm
  * CMA-ES
  * NSGA-II
    - non-dominated sorting
    - crowding distance
\subsubsection{Neural Architecture Search (NAS)}

\subsection{Multi-Objective Optimization}
- intro

>>>>

\section{Introduction}
Tabular Data
- most common type of data
- bad performance of deep learning models on tabular data, recent research suggests that heavy regularisation is necessary

regularisation
- LM: ridge (L2) + lasso (L1)
  * ridge: overcome multi-collinearity by pulling coeffs close to 0
  * lasso: variable selection by setting coeffs = 0
- NN:
  * L2 regularisation implicitly included in SGD when using weight decay (pull params towards 0) -> does this combat multi-collinearity as well or serve another purpose?
  * L1
    + key claim of DL: feature selection obsolete, network finds important ones itself
    + still, feature usually always has some impact (back this up), no explicit feature selection
    + explicit feature selection simply by not inluding a feature
  * another classical NN regularisation technique: dropout against co-adaptation
  * early stopping

@@

@@

\subsection{Automated Machine Learning (AutoML)}
\subsubsection{Hyperparameter Optimization (HPO)}
- grid + random search
- Bayesian optimisation
-> both unsuitable for our task
  + would be ok for weight decay (L2) + dropout optim
  + but: approaches for feature selection (L1) not feasible
    (a) 0-1 penalty on included features added to loss, problems:
      - how to choose regularisation parameter?
      - not all features equally important -> weighted 0-1 loss? how to choose weights?
    (b) directly optimise over binary hpyercube -> how to optim over non-ordinal discrete space?
-> evolutionary algorithms can be a solution for these types of problems
  * CMA-ES
  * NSGA-II
    - non-dominated sorting
    - crowding distance
\subsubsection{Neural Architecture Search (NAS)}
not sure if super relevant as I don't use a specific NAS technology (e.g. one-shot, etc.) but simply optimise over \# layers + \# nodes as HPs

\subsection{Multi-Objective Optimization}
- problem: all aforementioned approaches are a-priori approaches -> we choose best HPs (weight decay, features used, dropout) w.r.t. performance
- intro MOO
